Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-08-18 main.tex
Typesets with ACM... need to polish.

\documentclass[10pt,twocolumn,letterpaper]{article}
% ICCV Rules:
% 8 page limit (6 free + 2 paid)
% 10MB pdf file size limit
% 30MB supplementary materials file size limit (PDF or ZIP)

\usepackage{cvpr}
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{subfigure}

% Needed for getting formulas in dia diagrams.
\usepackage{pstricks}
\usepackage{tikz}

\usepackage{mydefs}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{184} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready

\hyphenation{under-determined}
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

\title{\vspace{-0.75in} Parallelization of Fast $\ell_1$-Minimization for Face Recognition}

% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both

\author{Andrew Wagner\\
University of Illinois at Urbana-Champaign\\
{\small awagner@illinois.edu}
\and
Victor Shia\\
University of California Berkeley\\
{\small vshia@eecs.berkeley.edu}
\and
Allen Yang\\
{\small yang@eecs.berkeley.edu}
\and
Mark Murphy\\
{\small mjmurphy@eecs.berkeley.edu}
\and
Yi Ma\\
University of Illinois at Urbana-Champaign\\
{\small yima@illinois.edu}
}

@@

\vspace{-0.06in}
{\small
\bibliographystyle{ieee}
\bibliography{faces-short}
}

>>>>

\documentclass[preprint]{sigplanconf}

%\usepackage{cvpr}
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{subfigure}
\usepackage{pstricks}
\usepackage{tikz}
\usepackage{mydefs}

% A few things in cvpr style file but not in ACM...
\def\eg{\emph{e.g.\ }} 
\def\ie{\emph{i.e.\ }}

\hyphenation{under-determined}
\begin{document}

\conferenceinfo{PPoPP '12}{Feb. 29, New Orleans.} 
\copyrightyear{2012} 
\copyrightdata{[to be supplied]}

\titlebanner{REVIEW COPY; PLEASE TO NOT REDISTRIBUTE}        % These are ignored unless
%\preprintfooter{short description of paper}   % 'preprint' option specified.

\title{Parallelization of Fast $\ell_1$-Minimization for Face Recognition}

%\authorinfo{Name1}
           %{Affiliation1}
           %{Email1}
%\authorinfo{Name2\and Name3}
           %{Affiliation2/3}
           %{Email2/3}
\authorinfo{Andrew Wagner\and Yi Ma}
			{University of Illinois at Urbana-Champaign}
			{\{awagner,yima\}@illinois.edu}
\authorinfo{Victor Shia\and Allen Yang\and Mark Murphy}
			{University of California Berkeley}
			{\{vshia,yang,mjmurphy\}@eecs.berkeley.edu}
%\authorinfo{Allen Yang}
			%{University of California Berkeley}
			%{yang@eecs.berkeley.edu}
%\authorinfo{Mark Murphy}
			%{University of California Berkeley}
			%{mjmurphy@eecs.berkeley.edu}
%\authorinfo{Yi Ma}
			%{University of Illinois at Urbana-Champaign}
			%{yima@illinois.edu}

@@

\bibliographystyle{abbrvnat}
\bibliography{faces-short}
